---
title: "PmlReport"
output: html_document
---
1. Preparing. Loading libraries, set seed and working directory.


```{r}
library(ggplot2)
library(caret)
set.seed(123)
setwd("/Users/mamadashi/Data sciense/pml/R")
```
2. Reading data.
```{r}
data <- read.csv("pml-training.csv")
predict <- read.csv("pml-testing.csv")
```

3. Spliting data into training/test

```{r}
index <- createDataPartition(y = data$classe, p = 0.95, list = FALSE)
train <- data[index,]
test <- data[-index,]
```

4. Analyse dataset. 
  Identification of near zero variance predictors.
```{r}
  nzv <- nearZeroVar(train, saveMetrics = TRUE)
  subset(nzv, nzv==FALSE)
```
Feature Plot
```{r}
featurePlot(x = train[, c("roll_belt",
                          "pitch_belt",
                          "yaw_belt",
                          "roll_forearm",
                          "pitch_forearm",
                          "yaw_forearm",
                          "roll_dumbbell",
                          "pitch_dumbbell",
                          "yaw_dumbbell",
                          "roll_arm",
                          "pitch_arm",
                          "yaw_arm")], y= train$class, plot="pairs");
```


5. Building some models on training set.
 Use "k-nearest neighbors" method as most suitable for classification.
 Model 1. Use some predictors that looks like more valuable
```{r}
fit1 <-  train(classe ~ roll_belt+
               pitch_belt+
               yaw_belt+
               roll_forearm+
               pitch_forearm+
               yaw_forearm+
               roll_arm+
               pitch_arm+
               yaw_arm
             , data = data, method = "knn")
fit1
plot(fit1)
```
Model 2. Adding more predictors.
```{r}

fit2 <- train(classe ~ roll_belt+
               pitch_belt+
               yaw_belt+
               roll_forearm+
               pitch_forearm+
               yaw_forearm+
               roll_dumbbell+
               pitch_dumbbell+
               yaw_dumbbell+
               roll_arm+
               pitch_arm+
               yaw_arm
             , data = data, method = "knn")
fit2
plot(fit2)
```

Model 3. Using preprocessing.

```{r}
fit3 <- train(classe ~ roll_belt+
               pitch_belt+
               yaw_belt+
               roll_forearm+
               pitch_forearm+
               yaw_forearm+
               roll_dumbbell+
               pitch_dumbbell+
               yaw_dumbbell+
               roll_arm+
               pitch_arm+
               yaw_arm
             , data = train, method = "knn", preProcess =
               c("center","scale"))
fit3
plot(fit3)
```

6.Test with test data.

Model 3 is the best one, so test it with test data.

```{r}
r <- predict(fit, newdata = test)
cm <- confusionMatrix(r, test$classe)
cm

```

7. Predict
```{r}
r <- predict(fit, newdata = predict)
predict[, "classe"] <- r
predict[, c("problem_id", "classe")]
```

